Dynein project log

### 2017-02-08 thesis_stuff/thesis_stuff.tex

>>>>

\subsection{Single-Molecule Analysis of Dynein processivity and Stepping Behavior}
2006 paper on single-molecule analysis of step sizes of dynein. Might have in-vivo velocity information.

Cool asside: Dynein can be dissociated from microtubules by adding 5mM ATP. This makes sense, since unbinding rate is proportional to ATP concentration.\\

Report a velocity of $85\pm30$ nm/s. Run length of $1.9\pm0.2\mu m$. Measurements done at $1mM ATP$.\\

Required for walking: two motor domains, but not cargo binding or associated chains.\\

Step length assay conducted at $4 \mu M$ ATP, roughly three orders of magnitude less than \textit{in vivo} ATP concentration.\\

Head steps are roughly 8nm, but motor movements per step are 0 for nonmoving and 16-18 for moving motor. This means that our average step size should be about 16nm.\\

Dwell time: probably the average time a domain is bound to the MT? IE the total step time? Although perhaps they only measure dwell times when they are especially long, since the average looks to be around 2s, or ten dynein steps.\\

Stepping rate of 0.13 per second per $\mu M$ ATP. Ten steps per second, consistent with velocity.\\

Forward stepping probability: 0.8\\

Propose the original ``alternate shuffling''/''hand-over-hand'' mechanism, where each head moves past the other, and the tail/centroid moves a half of each motor domain's movement.\\

\subsection{ATP concentration papers}
\paragraph{The Contents of Adenine Nucleotides, Phsphagens and some Glycolytic Intermediates in Resting Muscles from Vertebrates and Invertebrates -- 1975}

Found the following:

\begin{center}
  \begin{tabular}{| l | l |}
    \hline
    Organism & ATP\\ \hline
    Locust flight muscle & 5.8mM\\ \hline
    Rosechafer flight muscle & 8.5mM\\ \hline
    Dogfish white muscle & 4.18mM\\ \hline
    Lab rat thigh & 6.23mM\\ \hline
    Lab rat kidney & 1.71mM\\ \hline
  \end{tabular}
\end{center}

\paragraph{Diversity in ATP concentrations in a single bacterial cell population revealed b quantitate single-cell imaging}

Report $1.54\pm1.22$ mM\\

\paragraph{Bionumbers: http://bionumbers.hms.harvard.edu/search.aspx?log=y\&task=searchbytrmorg\&trm=atp+concentration\&org=}

Growing E. coli: 9.6 mM\\
human blood cell: 1.61 mM\\
Maize: 0.5-1.2 mM\\
